A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotides distribution

### 2013-03-12 ISMB/results_ISMB.tex
updated

  Figure~\ref{fig:nb_sols_entropy} shows the number of correct
solutions \highlight{as their average sequence identity. Since \ourprog
only influences the distribution of nucleotides inside stacked base pairs, 
we consider the \GCContent only inside those base pairs.}
  %entropy and positions inside base pairs entropy, since 
%\ourprog  only influences the distribution of nucleotides inside 
%stacked base pairs. 
The most constraining factor for generating valid
 solutions seems to be  low \GCContent and the percentage of free nucleotides.

@@

\highlight{
Figure~\ref{fig:nb_sols_entropy} shows the number of solutions generated (i.e. sequences with a MFE structure identical to the target structure) and the average sequence identity of the sequences. Here, we note that low {\GCContent}s have a strong (negative) influence on the number of sequences generated, and in parallel also affect negatively the sequence diversity. This observation emphasizes the difficulty to  design sequences with low \GCContent. Once again, large percentages of free nucleotides increase the difficulty of the task.

>>>>

  %entropy and positions inside base pairs entropy, since 
%\ourprog  only influences the distribution of nucleotides inside 
%stacked base pairs.

@@

\highlight{
Figure~\ref{fig:nb_sols_entropy} shows the number of solutions generated (i.e. sequences with a MFE structure identical to the target structure). Here, we note that low {\GCContent}s have a strong (negative) influence on the number of sequences generated, and in parallel also affect negatively the sequence diversity. This observation emphasizes the difficulty to  design sequences with low \GCContent. Once again, large percentages of free nucleotides increase the difficulty of the task.
